Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis

### 2020-03-12 Tex/CAV2019/CAV2020_rebuttal_rev0.txt

SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro
Category: Industrial Experience Reports & Case Studies

================REBUTTAL====================================

*****************Reviewer 1*********************************
Q2: Isn't CBMC a model checker for C/C++? Can't you use directly an SMT solver like Z3?
Answer: The algorithm was written in Language C (we are sorry, but it seems that this information is not present at the peper), and the code was the same for all verifier engines (CBMC, ESBMC, and CPAchecker). This technique (the use of formal synthesis in order to obtain the optimal sizing of solar PV systems) was one part of a Thesis defended by one author in January of 2020; and we treid different verifier engines (and solvers), but the combination ESBMC with Z3 version 4.7.1 presented an internal failure in all case studies. It corresponds to a ’bug’ in the Z3 solver which will require an updated version of ESBMC to fix it.

*******************Reviewer 2*******************************
Question for authors #1: Currently, the CEGIS loop results in a *single input* being added at each iteration. This may require a large number of iterations for the synthesis component to produce a candidate that succeeds in the verifier. Is there a more *general* constraint that the verifier can produce, to help the synthesizer more quickly rule out bad candidates?
Answer: We realized that just after the paper submission. In a updated version of the algorithm (not the one presented at this paper), we inclued a minimum cost for the beginning of iterative loop. This cost is the lowest among the list of equipment used, considering a configuration of just one solar PV panel, one charge controller, one battery, and one inverter. Indeed, if we use a bigger list of equipment then the time to result is bigger.

Question for authors #2: Where does the verification step occur in Algorithm 1? Unless I'm missing something, the VERIFY and SYNTHESIZE phases don't show up explicitly in Algorithm 1.
Answer: We will try to explain better here: the SYNTHESIZE phase is obtained by an feasible combination of equipment that meet the properties collected from the electrical requirements of the equipment itself (power, current or voltage). As told at the paper, this phase produces one feasible solution at line 20. The VERIFY phase is the responsible to obtain the lowest cost (minimum cost is the optimization objective function) considering the iterative steps taken from the 'for' loop that goes from line 6 to 22 of the algorithm 1. The code will cause an FAIL when the optimal sizing is found or when there is not feasible solution (SUCCESS).

Question for authors #3: My understanding is that the verification step uses a model checker. What exactly does the model look like?
Answer: Yes, we use model checking. The model (constraint and properties) is obtained from the math model used for the sizing, from the electrical characteristic of the equipment (in order to combine electrical compatibility among equipment, as current, voltage, or power), from the 'assumes' included explicitly at the algorithm 1, and from the objective function (minimum cost of the feasible PV sizing solution). We created a specific page for the C^(not)P, after the paper was finished, and it is present in:

Question for authors #4: In regards to the mismatched Windows/Ubuntu machine specs in section 4.3, why couldn't you just use separate Windows/Ubuntu VMs on the same host machine?
Answer: Yes, the ideal should be to use the same hardware configuration for the tests. However we got restrictions related to the licence for the HOMER Pro, and we did not have autonomy to change the Linux VM machine because it was shared with other PhD students with lots of experiments running.

****************REVIEWER 3************************************
1. You mention in the last sentence of Section 2 that the requirements involve non-linear equations. In many cases, it is sufficient for the requirements to be monotonic (for example, doubling the solar irradiance will conceivably always increase power output, even if it does not double it, or increasing panel efficiency will necessarily increase power output). Have you thought of exploiting such monotonicity properties for the purposes of optimization?

2. Your choice of words in Figure 2 (and elsewhere in the paper) is a bit non-standard. In traditional usage, failure to verify a candidate program results in a counter-example and successful verification results in termination of the CEGIS loop.

3. In any case, why do you describe the algorithm as a CEGIS loop when it could more simply be described as iteratively increasing the target cost and using a constraint solver to determine whether the target cost is feasible?

*********************REVIEWER 4*******************************
However, I have some reservations about the technical approach. First, the target problem here is one of optimization, but the synthesis algorithm does not model the optimality objective explicitly, instead relying on standard CEGIS. A quantitative synthesis approach, which casts synthesis as constrained optimization over a space of programs, seems more appropriate. Second, the application demands reasoning about constraints in nonlinear real arithmetic, which is a hard problem. It is not clear how this problem will be solved.

Finally, the paper claims that the method does can lead to "more accurate results than existing commercial tools." However, this claim is not validated through an empirical evaluation.

*******************************************************************
*****************ORIGINAL COMMENTS*********************************
*******************************************************************

----------------------- REVIEW 1 ---------------------
SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro

----------- Overall evaluation -----------
SCORE: 1 (weak accept)
----- TEXT:
This (tool) paper describes a new application area for SMT-based synthesis in the domain of photovoltaic systems. The method is a standard CEGIS approach + constantly increasing the allowed cost as long as there is no feasible solution. The case studies (based on the real data of electrical load) compare the developed tool to a commercial software called Homer.

I appreciate the application of formal methods in industrial applications (especially for clean and affordable energy), and believe that the paper (while not in the main focus of the conference) could be a nice addition to CAV.

One drawback is that I could not really see a conclusive answer to EG3 (how does the is formal synthesis tool compare to a specialized simulation tool?). In particular, do the case studies (except for #2) have deployed systems that allow to validate the synthesized results?

For rebuttal:
Q1: Is this optimization problem beyond the scope (or ability) of probabilistic programming?
Q2: Isn't CBMC a model checker for C/C++? Can't you use directly an SMT solver like Z3?

----------------------- REVIEW 2 ---------------------
SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro

----------- Overall evaluation -----------
SCORE: 1 (weak accept)
----- TEXT:
======= Paper Summary =======

This paper presents a program synthesis-based approach for solving the optimal PV sizing problem, which consists of selecting optimal parameters for photovoltaic (PV) systems. The tool uses a CEGIS loop architecture, with a synthesizer producing a candidate solution that is correct for a finite number of inputs, and a verifier checking whether the candidate is correct for *all* inputs. To evaluate the tool, the authors apply it to real-world electrical systems, including one in the Amazonas State, Brazil.

======= Contributions =======

The paper presents the following contributions:

#1. The paper is one of the first to apply formal methods to PV system design.

#2. The approach translates problems in the PV design space into a form that can be tackled using efficient off-the-shelf verification tools.

#3. The paper contains meaningful real-world applications of the approach, and discusses ways to improve on the state of the art in this area.

======= General Questions/Comments =======

Cons:
- The techniques are not particularly novel (CEGIS, model-checking, etc. are used in a mostly black-box way).
- There are some shortcomings and unclear components of the algorithm. For example, the CEGIS loop could iterate a huge number of times, due to the simple strategy for adding inputs to the synthesis component. Additionally, the verification/synthesis components are not described in detail.

Pros:
- The paper describes a tool which targets a vital real-world problem. I think it's fantastic to see researchers applying formal methods in areas related to renewable energy.
- The overall CEGIS approach seems promising, and the experimental results seem good.

Question for authors #1: Currently, the CEGIS loop results in a *single input* being added at each iteration. This may require a large number of iterations for the synthesis component to produce a candidate that succeeds in the verifier. Is there a more *general* constraint that the verifier can produce, to help the synthesizer more quickly rule out bad candidates?

Question for authors #2: Where does the verification step occur in Algorithm 1? Unless I'm missing something, the VERIFY and SYNTHESIZE phases don't show up explicitly in Algorithm 1.

Question for authors #3: My understanding is that the verification step uses a model checker. What exactly does the model look like?

Question for authors #4: In regards to the mismatched Windows/Ubuntu machine specs in section 4.3, why couldn't you just use separate Windows/Ubuntu VMs on the same host machine?

Suggestions for improvement:
- I don't quite understand why a *counterexample* from the verifier represents "success" of the tool. Usually a generated counterexample would be sent back to the synthesizer to help improve the next generated candidate. It would be helpful if this is clarified in the next revision.
- It would be helpful if the "PV sizing" problem could be more precisely articulated.

======= Conclusion =======

This is an interesting application of program synthesis to an important problem in the real world. Although the tool primarily uses existing techniques, it seems to perform well compared to existing tools in the PV design domain.

======= Nitpicks =======

- page 2: "reasoning of a model" --> "reasoning about a model"
- page 7: "ensure that the approach is sound" --> "ensure that the solution is sound"
- page 10: "HOME Pro was unable" --> "HOMER Pro was unable"
- page 10: "but not sound as our method" --> "but not sound, as is our method"
- page 10: "approach to pursuit the" --> "approach to pursue the"
- page 10: "which is far detailed" --> "which is far more detailed"

----------------------- REVIEW 3 ---------------------
SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro

----------- Overall evaluation -----------
SCORE: -2 (reject)
----- TEXT:
Overview of the Paper
---------------------

The choice of optimal photovoltaic cells (in terms of weather, cost, efficiency, surface area, number of panels, etc.) is an important challenge in the widespread deployment of decentralized solar energy harvesting systems. This paper considers the use of CEGIS-based techniques in combination of program verifiers such as CPAchecker, CBMC, or ESBMC to make optimal decisions.

The algorithm takes as input a list of panel types and associated equipment, including batteries, controllers, inverters, and installation-specific details, such as weather data, power demand etc. The problem is to identify the most cost-effective installation which satisfies the given requirements. The core technique appears to involve repeatedly checking whether a solar panel configuration exists with a given target cost, which starts at 0 and iteratively increases until it reaches some pre-defined maximum. In each step, the installation parameters are non-deterministically chosen, and a program verifier determines whether there is a choice of these parameters which leads to the requirements being satisfied.

Experiments are presented which evaluate the system on a selection of six installation requirements. CBMC is able to generate an optimal configuration for all but one of the settings.

Appraisal
---------

It is unclear to me that CAV is an appropriate venue for such a paper. The specific domain of solar photovoltaics is outside my area of expertise, and I presume, outside the expertise of the average CAV attendee. The paper seems better suited to a conference on smart cities, IoT, or energy systems.

One potential reason to accept this at CAV would be if the technique involved some novelty at the level of the optimization algorithm. Examples include (a) a non-trivial use of CEGIS to perform optimization, (b) a close synergy between program synthesis and the application domain of photovoltaic cells, or (c) a failure of off-the-shelf numerical optimizers to succeed at this task. Unfortunately, the paper could not convince me of this.

I therefore do not vote for this paper to be accepted.

Questions and Comments for the Authors
--------------------------------------

1. You mention in the last sentence of Section 2 that the requirements involve non-linear equations. In many cases, it is sufficient for the requirements to be monotonic (for example, doubling the solar irradiance will conceivably always increase power output, even if it does not double it, or increasing panel efficiency will necessarily increase power output). Have you thought of exploiting such monotonicity properties for the purposes of optimization?

2. Your choice of words in Figure 2 (and elsewhere in the paper) is a bit non-standard. In traditional usage, failure to verify a candidate program results in a counter-example and successful verification results in termination of the CEGIS loop.

3. In any case, why do you describe the algorithm as a CEGIS loop when it could more simply be described as iteratively increasing the target cost and using a constraint solver to determine whether the target cost is feasible?

----------------------- REVIEW 4 ---------------------
SUBMISSION: 22
TITLE: Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison
AUTHORS: Alessandro Trindade and Lucas Cordeiro

----------- Overall evaluation -----------
SCORE: -2 (reject)
----- TEXT:
Summary:

The paper is a case study of the application of program synthesis to obtaining the optimal sizing of solar photovoltaic (PV) systems.

Evaluation:

The paper is on an interesting topic. Prior work has sought to verify the correctness of PV panels. The automatic synthesis of safe-by-construction parameters of PV panels is a natural next step. Also, the authors have taken care to use real data from the Amazonas state.

However, I have some reservations about the technical approach. First, the target problem here is one of optimization, but the synthesis algorithm does not model the optimality objective explicitly, instead relying on standard CEGIS. A quantitative synthesis approach, which casts synthesis as constrained optimization over a space of programs, seems more appropriate. Second, the application demands reasoning about constraints in nonlinear real arithmetic, which is a hard problem. It is not clear how this problem will be solved. Finally, the paper claims that the method does can lead to "more accurate results than existing commercial tools." However, this claim is not validated through an empirical evaluation.

------------------------------------------------------

### 2020-04-07 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
paper update 2020

%% bare_jrnl.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/pkg/endfloat
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

@@

% The paper headers
\markboth{IEEE Transactions on Sustainable Energy,~Vol.~XX, No.~YY, September~2019}%
{Trindade and Cordeiro: An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

@@

Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted. If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost. Note that in this study, our focus is not on new criteria or even optimization objectives. Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.

@@

Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to our synthesis engine in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars.

With respect to power reliability, this work will rely on the critical period solar 
energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
The usual way is to use loss of load probability (LOLP) or loss of power 
supply probability (LPSP). However, we are neither considering site characteristics nor the load changes over time, 
which demands historical data, the reliability analysis will be developed only 
by the critical period method of PV sizing.
%
Regarding financial analysis:
\begin{itemize}
	\item LCC lifetime considered: $20$ years;
	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}. This cost includes the battery replacement based on its lifetime ($4$ years for lead-acid batteries), plus inverters and controller replacement (every $10$ years). Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis.
\end{itemize}

@@

Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common to lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).

@@

Concerning the charge controllers, as we reported in the previous section, HOMER Pro does not include it as an explicit equipment in its mathematical model; only our synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOME Pro.

>>>>

\documentclass[journal]{IEEEtran}

\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

% The paper headers
\markboth{IEEE Transactions on Sustainable Energy,~Vol.~XX, No.~YY, April~2020}%
{Trindade and Cordeiro: An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

@@

Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS)~\cite{AbateCAV2018} for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted. If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost. Note that in this study, our focus is not on new criteria or even optimization objectives. Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.

@@

Regarding the line $2$ of Algorithm~\ref{alg:verification-algorithm}, a list of forty equipment from ten different manufacturers was provided to our synthesis engine in order to allow the choice of every item of PV sizing. Data sheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. All this data is available online\footnote{https://drive.google.com/file/d/1xZtAR4Wvgfqgox2PgySuPP-fZ9OA1u1j/view?usp=sharing}.

With respect to power reliability, this work will rely on the critical period solar 
energy method~\cite{Pinho} as described in Section~\ref{sec:sizing}. 
The usual way is to use loss of load probability (LOLP) or loss of power 
supply probability (LPSP). However, we are neither considering site characteristics nor the load changes over time, 
which demands historical data, the reliability analysis will be developed only 
by the critical period method of PV sizing.
%
Regarding financial analysis:
\begin{itemize}
	\item LCC lifetime considered: $20$ years;
	\item Installation costs: includes delivery in the isolated community and installation costs itself, $5$\% of total cost~\cite{Agrener2013};
	\item Value of the discount rate or interest rate: $10$\%, which is a good rate considering financial investments in developing countries;
	\item Operation and maintenance annual costs: based on PV projects of similar size in the Amazon region of Brazil, will be adopted the value of US\$ 289.64~\cite{Agrener2013}. This cost includes the battery replacement based on its lifetime, plus inverters and controller replacement (every $10$ years). We adopted lead-acid batteries, the cheapest and most common kind used nowadays; and it means a $4$ years lifetime. Therefore, it will be performed three battery bank and one inverter-controller replacements during the LCC analysis. Worth to mention that  those data can be adjusted in our algorithm.
\end{itemize}

@@

Regarding all case studies, it was defined that the minimum state of charge of batteries is $75$\% (with DOD maximum of $25$\%, which is common adopted for lead-acid batteries), the voltage of the system is set in $24$ V DC (the most common as well, but the value can be adjusted to $12$ or $48$ V at the code), and the AC voltage from the inverter is $127$ V (Brazilian standard).

@@

Concerning the charge controllers, as we reported in the previous section, HOMER Pro does not include it as an explicit equipment in its mathematical model and does not includes the cost for the charge controller; only our synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOME Pro.
